\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-03-04 manuscript/manuscript.tex
eas

@@

Using simulation, we have shown that given a large enough sample of a time 
series, the block 
bootstrap KS test can appropriately fail to reject the null hypothesis when the
series follows the null distribution. In addition, when the marginal
distribution is not
the one hypothesized, the test is powerful. It requires a larger sample size 
than basic bootstrap to avoid either type I or type II errors. Unsurprisingly,
the method performs better as the temporal dependence gets weaker. Through
simulation studies with Normal and Gamma-distributed data, we have shown that
that the method is robust. We have also 
demonstrated possible applications of this method to precipitation and 
stock return data. This method can be used for any study where the goal is
to see if a time series follows a hypothesized distribution and the parameters
are unknown or unspecified. Future studies could apply the method showcased
in this paper to fields like earthquake prediction and astronomy.

>>>>

Annual temperature minimums were also recorded from Central Park, and the
same method comparison was applied to this series. We found that our method
yields a p-value of 0.0015, Babu's method yields a p-value of 0.2747, and
the parametric method yields a p-value of 0.0002.

\subsection{Temperature in Eastern Asia}
\label{sec:temperature}

Annual maximums of daily maximum (TXx) and minimum (TNx) temperatures, and annual 
minimums of daily maximum (TXn) and minimum (TNn) temperatures were collected
for 60 years from 44 locations in Eastern Asia.

@@

Using simulation, we have shown that given a large enough sample of a time 
series, the block 
bootstrap KS test can appropriately fail to reject the null hypothesis when the
series follows the null distribution. In addition, when the marginal
distribution is not
the one hypothesized, the test is powerful. It requires a larger sample size 
than basic bootstrap to avoid either type I or type II errors. Unsurprisingly,
the method performs better as the temporal dependence gets weaker. Through
simulation studies with Normal and Gamma-distributed data, we have shown that
that the method is robust. We have also 
demonstrated possible applications of this method to climate and financial data.
Although in many cases, the conclusions may not differ between our method
and other bootstrap KS tests, the p-values are different enough where in a case
where the temporal dependence in the data is more extreme, conclusions could
be drastically different if a different method is used.
This method can be used for any study where the goal is
to see if a time series follows a hypothesized distribution and the parameters
are unknown or unspecified. Future studies could apply the method showcased
in this paper to fields like earthquake prediction and astronomy.
